Msc Thesis Figures

### 2020-08-21 docs/msc_thesis_figures.Rmd
add docs to list - test

fig_1_historic <- joined %>% 
  filter(climate == "none") %>% 
  group_by(scenarioId, species, iteration) %>% 
  group_modify(~mutate(.x , baseline = subset(.x, timestep == 1990)$sum_cur, 
                       the_diff = ((sum_cur-baseline)/baseline)*100 )) %>% 
  ggplot(aes(x=timestep, y=the_diff, col=source)) +
  scale_color_manual(values=c('#d8b365','#5ab4ac'), 
                     labels = c("Model", "Observation")) +
  geom_smooth(aes(group = sce), method = "glm", se=FALSE) +
  scale_linetype_manual(values = c(1,3,2,5))+
  geom_point(aes(group = sce)) +
  facet_wrap(~species, scales = "fixed") +
  labs(y = "Current flow (% Change)",
       x = "Year",
       col = "Source") +
  NULL
fig_1_historic
ggsave(fig_1_historic,
       filename = "../thesis/figures/connectivity_decrease_x5species_historic.png",
       width = the_width, height = the_height, dpi = the_dpi)
```

>>>>

fig_1_historic <- joined %>% 
  filter(climate == "none") %>% 
  group_by(scenarioId, species, iteration) %>% 
  group_modify(~mutate(.x , baseline = subset(.x, timestep == 1990)$sum_cur, 
                       the_diff = ((sum_cur-baseline)/baseline)*100 )) %>% 
  ggplot(aes(x=timestep, y=the_diff, col=source)) +
  scale_color_manual(values=c('#d8b365','#5ab4ac'), 
                     labels = c("Model", "Observation")) +
  geom_smooth(aes(group = sce), method = "glm", se=FALSE) +
  scale_linetype_manual(values = c(2,3,2,5))+
  geom_point(aes(group = sce)) +
  facet_wrap(~species, scales = "fixed") +
  labs(y = "Current flow (% Change)",
       x = "Year",
       col = "Source") +
  NULL
fig_1_historic
ggsave(fig_1_historic,
       filename = "../thesis/figures/connectivity_decrease_x5species_historic.png",
       width = the_width, height = the_height, dpi = the_dpi)
```
